% the acknowledgments section
Honestly the Ph.D. can be isolating, but luckily I had support from many people and friends that gave me strength to pull through.
First and foremost, I would like to thank Professor Vecitis for accepting me into his group, and giving me all the support needed during this time. Chad crafted the work presented here with his ingenious way of thinking. Over the last five years, Chad has become a friend and a great advisor both within and outside research---it is a true pity that SEAS let him go. I also want to thank Professor Sunderland for ''adopting'' me into her lab, allowing me to use her research space and giving me research advice on the nanotoxicity part of this thesis. The scientific work presented here would not have materialized without the help of the following people: Professor Grossman with his insight on graphene oxide, Sauro Succi and Andrea Montessori with their experience in computational fluid dynamic methods, Paula Arribas and Luis Cruzado with their extended knowledge in the membrane field, and the research staff at CNS with their continuous support for the characterization of nanomaterials. During the last part of this thesis regarding toxicity, I also had the wonderful support of Professor Demokritou and Dr. Bitounis. Throughout my time here, I have had the opportunity to work next to great friends---Greg, Andrea, Marielle, and Jenny thank you for being awesome labmates and mentors.\\
Apart from research, what we should cherish are human connections. I was so lucky to meet the ''tensome'' group. We basically met at the very beginning of the Ph.D. and during my time here in Cambridge, we fostered a friendship that I hope will last for many years; we took care of each other, we celebrated each other's successes, and we listened to each other venting and ranting. We went through hard times and we knew that we always had somebody ready to support and help us. I feel so privileged to know you guys! During my time at Harvard I also have had the wonderful opportunity to be part of two organizations that offer the distractions needed to carry out a Ph.D. First, the Harvard Italian Student Society made me feel like I was in Italy when I was homesick, and second, the Harvard Mountaineering Club made me feel alive. 
Finally, I would like to thank my parents for giving me the best thing they could have given me---the power of self-determination. I want to also thank my sister for being the closest person I have and a person I can always count on.

